Using tours to visually investigate properties of new projection pursuit indexes with application to problems in physics

### 2019-01-11 scagnostics.Rmd
tweaks to last paragraph of intro

The paper investigates the behavior of these newly-defined indexes. Section \ref{sec:construct} discusses index construction, and how they fit into the guided tour. Section \ref{sec:investigate} investigates the behavior of the indexes, particularly in relation to optimization. The new guided tour methods are applied to an example where the posterior distributions from physics models (Section \ref{sec:phys}) are explored.

>>>>

The paper investigates the behavior of these indexes. Section \ref{sec:construct} discusses index construction, and how they fit into the guided tour. Section \ref{sec:investigate} investigates the behavior of the indexes, explored primarily using tour methods (@As85, @BCAH05, @CBCH94). The new guided tour with these indexes are applied to two examples from physics models (Section \ref{sec:phys}).
